\documentclass[12pt]{ctexart}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{enumitem}

\title{EMPLOYMENT CONTRACT}
\author{}
\date{}

\begin{document}

\maketitle

\noindent This Employment Contract (the "Contract") is made and entered into as of \underline{\hspace{3cm}} by and between:

\vspace{0.5cm}

\noindent \textbf{PARTY A (Employer):} XXX Company

\noindent \textbf{PARTY B (Employee):} John Doe

\vspace{0.5cm}

\section*{POSITION}
Party B shall serve as Software Engineer at Party A.

\section*{PROBATION PERIOD}
The probation period shall be 3 months from the commencement date of employment.

\section*{COMPENSATION}
Party A shall pay Party B a monthly salary of \$2000, payable on the last working day of each month.

\section*{TERMS AND CONDITIONS}
\begin{enumerate}[leftmargin=*,label=\arabic*.]
    \item Party B shall comply with all company rules, regulations, and policies during the employment period.
    
    \item This Contract shall automatically terminate upon expiration. For early termination, either party must provide 30 days written notice to the other party.
    
    \item Any matters not covered by this Contract shall be resolved through mutual agreement between both parties.
\end{enumerate}

\section*{GENERAL PROVISIONS}
\begin{itemize}[leftmargin=*,label={}]
    \item This Contract constitutes the entire agreement between the parties.
    \item Any amendments must be made in writing and signed by both parties.
    \item This Contract shall be governed by the laws of the jurisdiction where Party A is located.
\end{itemize}

\vspace{1cm}

\noindent \textbf{PARTY A (Employer):} \underline{\hspace{7cm}}

\noindent Signature: \underline{\hspace{7cm}}

\noindent Date: \underline{\hspace{7cm}}

\vspace{1cm}

\noindent \textbf{PARTY B (Employee):} \underline{\hspace{7cm}}

\noindent Signature: \underline{\hspace{7cm}}

\noindent Date: \underline{\hspace{7cm}}

\end{document}