\documentclass[12pt]{ctexart}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage[english]{babel}

\setmainfont{Times New Roman}
\setCJKmainfont{SimSun}

\title{Loan Agreement}
\author{}
\date{\today}

\begin{document}

\maketitle

\doublespacing

This Loan Agreement (the "Agreement") is made and entered into as of \underline{\hspace{3cm}} (the "Effective Date"), by and between:

\underline{\hspace{6cm}} ("Lender"), a company incorporated under the laws of \underline{\hspace{3cm}} with its registered office at \underline{\hspace{6cm}};

AND

\underline{\hspace{6cm}} ("Borrower"), a company incorporated under the laws of \underline{\hspace{3cm}} with its registered office at \underline{\hspace{6cm}}.

\section*{1. Loan Principal}
The Lender agrees to lend to the Borrower, and the Borrower agrees to borrow from the Lender, the principal sum of \underline{\hspace{3cm}} (the "Loan").

\section*{2. Interest}
\begin{enumerate}[label=2.\arabic*]
    \item The Loan shall bear interest at a rate of \underline{\hspace{3cm}}\% per annum.
    \item Interest shall be calculated on the basis of a 360-day year and the actual number of days elapsed.
\end{enumerate}

\section*{3. Term and Repayment}
\begin{enumerate}[label=3.\arabic*]
    \item The term of the Loan shall be \underline{\hspace{3cm}} months/years from the Effective Date.
    \item The Borrower shall repay the Loan in \underline{\hspace{2cm}} equal installments of principal plus accrued interest, payable on the \underline{\hspace{2cm}} day of each month, commencing on \underline{\hspace{3cm}}.
    \item The final payment shall include all outstanding principal and accrued interest.
\end{enumerate}

\section*{4. Security}
The Loan shall be secured by \underline{\hspace{6cm}} (the "Security"). The Borrower shall execute all necessary documents to perfect the Lender's security interest in the Security.

\section*{5. Prepayment}
\begin{enumerate}[label=5.\arabic*]
    \item The Borrower may prepay the Loan in whole or in part at any time upon \underline{\hspace{2cm}} days' prior written notice to the Lender.
    \item Any prepayment shall include all accrued interest and a prepayment fee of \underline{\hspace{3cm}}.
\end{enumerate}

\section*{6. Events of Default and Acceleration}
\begin{enumerate}[label=6.\arabic*]
    \item The following shall constitute events of default:
    \begin{enumerate}[label=(\alph*)]
        \item Failure to make any payment when due;
        \item Breach of any covenant or representation;
        \item Insolvency or bankruptcy proceedings;
        \item Any material adverse change in the Borrower's financial condition.
    \end{enumerate}
    \item Upon an event of default, the Lender may declare all outstanding amounts immediately due and payable.
\end{enumerate}

\section*{7. Fees and Taxes}
\begin{enumerate}[label=7.\arabic*]
    \item The Borrower shall pay all taxes, duties, and governmental charges relating to this Agreement.
    \item The Borrower shall reimburse the Lender for all reasonable legal and administrative expenses.
\end{enumerate}

\section*{8. Dispute Resolution}
\begin{enumerate}[label=8.\arabic*]
    \item Any dispute shall first be submitted to mediation in \underline{\hspace{3cm}}.
    \item If mediation fails, the dispute shall be resolved by arbitration under the rules of \underline{\hspace{3cm}}.
    \item The prevailing party shall be entitled to recover reasonable attorney's fees.
\end{enumerate}

\section*{9. General Provisions}
\begin{enumerate}[label=9.\arabic*]
    \item This Agreement constitutes the entire agreement between the parties.
    \item Any amendment must be in writing and signed by both parties.
    \item This Agreement shall be governed by the laws of \underline{\hspace{3cm}}.
\end{enumerate}

IN WITNESS WHEREOF, the parties have executed this Agreement as of the Effective Date.

\vspace{2cm}

\begin{tabular}{p{8cm}p{8cm}}
For and on behalf of Lender & For and on behalf of Borrower \\
\underline{\hspace{6cm}} & \underline{\hspace{6cm}} \\
Name: \underline{\hspace{5cm}} & Name: \underline{\hspace{5cm}} \\
Title: \underline{\hspace{5cm}} & Title: \underline{\hspace{5cm}} \\
Date: \underline{\hspace{5cm}} & Date: \underline{\hspace{5cm}} \\
\end{tabular}

\end{document}